Reinforcement Learning vs Imitation Learning for Surgical Action Prediction: A Comprehensive Evaluation Using Actual Trained Models

### 2025-05-27 corrected_publication_results/publication_tables.tex
add more experiments and evals

Ppo vs Sac & -0.031 & -4.472 & 0.000*** & -0.285 \\
Ppo vs Imitation Learning & -0.678 & -138.778 & 0.000*** & -8.830 \\
Sac vs Imitation Learning & -0.647 & -129.740 & 0.000*** & -8.255 \\

>>>>

Sac vs Ppo & 0.031 & 4.472 & 0.000*** & 0.285 \\
Sac vs Imitation Learning & -0.647 & -129.740 & 0.000*** & -8.255 \\
Ppo vs Imitation Learning & -0.678 & -138.778 & 0.000*** & -8.830 \\
